An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-01 poly-embed-journal/poly-embed-journal.tex
Updating examples section

Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.  Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube. \jessie{Added a bit discussing this, starting at ``the examples in ...''.}}
The examples in \S~\ref{sec:examples}, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
While this may sometimes yield a calibrated link, this is not always the case.
In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.
Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.

@@

@@

\btw{New (March 2 2021): adding Yutong's paper}
\subsection{Embedding Ordered Partitions}
\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.

An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
\begin{align*}
\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
\end{align*}
The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.

The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
\begin{equation}\label{eq:ww-hinge}
L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}

\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.

\begin{figure}[H]
		\centering
		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
	\label{fig:ordered-partition}
\end{figure}

\btw{Summer 2020: New example using hierarchical surrogate}
\subsection{Embedding hierarchical classifications}
Our final example comes from Ramaswamy et al.~\cite{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
\begin{equation}\label{eq:tree-loss-discrete}
	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
\end{equation}
In this setting, the outcomes $\Y$ are composed of all nodes in the tree and not just the leaves.

\begin{figure}
	\centering
		\includegraphics[width=0.7\linewidth]{tikz/example-tree-deeper.pdf}
		\caption{Tree $H$ with distribution $\vec p = (0, .2, .1, .4, .3)$. $\gamma^H(\vec p) = 3$.}\label{fig:example-tree-deeper}
\end{figure}

\begin{figure}
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree.pdf}
	\caption{3 node tree whose property we evaluate in next image.}
	\label{fig:3-node-tree}
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree-prop.pdf}
	\caption{Property elicited by unweighted 3-node tree.}
	\label{fig:3-node-tree-prop}
\end{minipage}
\end{figure}

In~\cite[Theorem 1]{ramaswamy2015hierarchical}, Ramaswamy et al. show the property $\gamma^H := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome, denoted $S_i(p)$, is greater than or equal to $1/2$.
They additionally note that this property is agnostic to the weight $W$ of the tree.
As before, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.
For an example, see Figure~\ref{fig:example-tree-deeper}, where predicting node $3$ minimizes the expected tree loss over the distribution $\vec p = (0, 0.2, 0.1, 0.4, 0.3)$.

Letting $h$ be the height of the tree $H$, Ramaswamy et al. present an embedding of $\ell^H$ that consists of learning $h$ $\abstain{1/2}$ embeddings, where the outcomes at the $j^{th}$ embedding are the nodes on level $j$ of the tree.
At each highest level, one proceeds down the path of the tree given by the prediction of the current abstain embedding.
If one predicts $\bot$ at level $j$, then we predict the node predicted at the $(j-1)^{st}$ level.

Note that the given \emph{Cascade Surrogate} of~\citet[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\citet{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.

It is worth noting that the cascade surrogate is not the always most efficient in terms of dimension.
For example, the cascading surrogate on the 3 node tree $H$ in Figure~\ref{fig:3-node-tree} takes two $1$-dimensional optimization problems for distributions $p$ such that $p_1 < 1/2$.
However, the property (Figure~\ref{fig:3-node-tree-prop}) elicited by tree distance for $H$ in Figure~\ref{fig:3-node-tree} is embeddable by a real-valued surrogate thanks to the characterization of \cite[\S~3]{finocchiaro2020embedding}, so one can see that the dimension cascade surrogate does not yield a tight bound.
This leaves the question of embedding dimension open for the hierarchical surrogate embedding the discrete tree loss $\ell^H$.

% \jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
% \proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.  Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
% \begin{align*}
% \R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
% \end{align*}
% The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
% \begin{equation}
% \ell^{top-k}(r,y) = \begin{cases}
% 0 & r_y = \bar r_{-y} + 1\\
% \bar r - \frac 1 k & r_y = 1\\
% 1 + \bar r & r_y = 0
% \end{cases}~,~
% \end{equation}
% where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
% }

>>>>

Our results give a framework to construct consistent surrogates and link functions for any discrete loss, but they also provide a way to verify the consistency or inconsistency of given surrogates.
Below, we illustrate the power of this framework with specific examples from the literature, as well as new examples.
In some cases we simplify existing proofs, while in others we give new results, such as a new calibrated link for abstain loss, and the inconsistency of the recently proposed Lov\'asz hinge.
\btw{RF: The top-k and hypercube/set examples (except abstain) have the link built in, e.g.\ as the sign function), and they just work around it.  Our results may suggest that it's worth thinking ``outside the box'' (HAH, genious...) and looking for embeddings which are not the hypercube. \jessie{Added a bit discussing this, starting at ``the examples in ...''.}}
The examples in \S~\ref{sec:examples}, with the exception of the abstain surrogate given by~\citet{ramaswamy2018consistent}, all present a surrogate that use the link $\psi: u \mapsto \sgn(u)$.
While this may sometimes yield a calibrated link, this is not always the case.
In fact, we will see that most of these examples do not yield calibrated surrogates, although proving that there is \emph{no} calibrated link for a given surrogate is quite difficult.
Our results suggest that it is possible that some of the given surrogates are calibrated, but perhaps one must use a nontraditional link in order to calibrate the loss, such as the thickening construction given here.
\citet{wang2020weston} apply the embedding framework to understand the Weston-Watkins hinge loss for ordered partitions.

@@

The embedding framework can also be applied to understand the hierarchical extension of the BEP surrogate given by~\citet{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
\begin{equation}\label{eq:tree-loss-discrete}
	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
\end{equation}
They generalize the BEP embedding to this problem and show their extension is consistent with respect to eq.~\ref{eq:tree-loss-discrete}; we can also verify this is an embedding and subsume their result through Theorem~\ref{thm:poly-ie-implies-consistent}.

@@

\btw{Yutong's paper commented out here}
%\subsection{Embedding Ordered Partitions}
%\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss.
%
%An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
%The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
%\begin{align*}
%\ell^\OP(S,y) &= |S_1| - 1 + \sum_{i=1}^{l-1} |S_1 \cup \ldots \cup S_{i+1}| \cdot \Ind{y \not \in S_1 \cup \ldots \cup S_i}~.~
%\end{align*}
%The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $S_1$.
%This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent, since the two are equivalent in Quadrant 1) with respect to $\ell^\OP$.
%
%The Weston-Watkins hinge loss takes predictions $u \in \reals^n$ and assigns loss
%\begin{equation}\label{eq:ww-hinge}
%L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
%\end{equation}
%
%\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in S_i$, we have $\varphi(S)_j = -(i-1)$.
%
%\begin{figure}[H]
%		\centering
%		\includegraphics[width=0.5\linewidth]{tikz/ordered-partition}
%	\caption{Level sets of the Weston Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.}
%	\label{fig:ordered-partition}
%\end{figure}

\btw{Hierarchical surrogate commented out; just mention in 7.1 since it builds off of that example.}
%\subsection{Embedding hierarchical classifications}
%Our final example comes from \citet{ramaswamy2015hierarchical}, who present a convex, calibrated surrogate for the hierarchical classification problem.
%Given a tree $H = ([n], E,W)$ over finite class labels, they consider the discrete loss 
%\begin{equation}\label{eq:tree-loss-discrete}
%	\ell^H(r,y) = \text{shortest path length in $H$ between $r$ and $y$}
%\end{equation}
%In this setting, the outcomes $\Y$ are composed of all nodes in the tree and not just the leaves.
%\begin{figure}
%	\centering
%		\includegraphics[width=0.7\linewidth]{tikz/example-tree-deeper.pdf}
%		\caption{Tree $H$ with distribution $\vec p = (0, .2, .1, .4, .3)$. $\gamma^H(\vec p) = 3$.}\label{fig:example-tree-deeper}
%\end{figure}
%\begin{figure}
%\begin{minipage}{0.45\linewidth}
%	\centering
%	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree.pdf}
%	\caption{3 node tree whose property we evaluate in next image.}
%	\label{fig:3-node-tree}
%\end{minipage}
%\hfill
%\begin{minipage}{0.45\linewidth}
%	\centering
%	\includegraphics[width=0.9\linewidth]{tikz/3-node-tree-prop.pdf}
%	\caption{Property elicited by unweighted 3-node tree.}
%	\label{fig:3-node-tree-prop}
%\end{minipage}
%\end{figure}
%In~\cite[Theorem 1]{ramaswamy2015hierarchical}, Ramaswamy et al. show the property $\gamma^H := \prop{\ell^H}$ is the deepest node $i$ in the tree $H$ such that the probability that node $i$ or one of its descendants is the outcome, denoted $S_i(p)$, is greater than or equal to $1/2$.
%They additionally note that this property is agnostic to the weight $W$ of the tree.
%As before, consider $p_i$ to be the probability that node $i$ is the ground truth label, and $S_i(p)$ to be the probability that node $i$ or one of its descendants is the ground truth.
%For an example, see Figure~\ref{fig:example-tree-deeper}, where predicting node $3$ minimizes the expected tree loss over the distribution $\vec p = (0, 0.2, 0.1, 0.4, 0.3)$.
%Letting $h$ be the height of the tree $H$, Ramaswamy et al. present an embedding of $\ell^H$ that consists of learning $h$ $\abstain{1/2}$ embeddings, where the outcomes at the $j^{th}$ embedding are the nodes on level $j$ of the tree.
%At each highest level, one proceeds down the path of the tree given by the prediction of the current abstain embedding.
%If one predicts $\bot$ at level $j$, then we predict the node predicted at the $(j-1)^{st}$ level.
%Note that the given \emph{Cascade Surrogate} of~\citet[Equation 2]{ramaswamy2015hierarchical} simply requires the use of a surrogate that is calibrated with respect to $\abstain{1/2}$, so we can use the BEP surrogate of~\citet{ramaswamy2018consistent} to concatenate $h$ $\ceil{\log_2(n)}$ dimensional embeddings for the tree loss, yielding an embedding for $\ell^H$.
%It is worth noting that the cascade surrogate is not the always most efficient in terms of dimension.
%For example, the cascading surrogate on the 3 node tree $H$ in Figure~\ref{fig:3-node-tree} takes two $1$-dimensional optimization problems for distributions $p$ such that $p_1 < 1/2$.
%However, the property (Figure~\ref{fig:3-node-tree-prop}) elicited by tree distance for $H$ in Figure~\ref{fig:3-node-tree} is embeddable by a real-valued surrogate thanks to the characterization of \cite[\S~3]{finocchiaro2020embedding}, so one can see that the dimension cascade surrogate does not yield a tight bound.
%This leaves the question of embedding dimension open for the hierarchical surrogate embedding the discrete tree loss $\ell^H$.
%% \jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
%% \proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.  Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
%% \begin{align*}
%% \R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
%% \end{align*}
%% The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
%% \begin{equation}
%% \ell^{top-k}(r,y) = \begin{cases}
%% 0 & r_y = \bar r_{-y} + 1\\
%% \bar r - \frac 1 k & r_y = 1\\
%% 1 + \bar r & r_y = 0
%% \end{cases}~,~
%% \end{equation}
%% where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
%% }
